A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-02-25 sections/model_overview/main.tex
Minor typo
Fix proselint failure by removing the word very from a comment
Additional changes in game section
- Replace waiting zone 1 with hospital
- Replace waiting zone 2 with parking space
- Use type 2 patients everywhere instead of ambulance patients

\begin{itemize}
    \item the decision makers of two Emergency Departments (EDs);
    \item the Emergency Medical Services (EMS) that distribute individuals in ambulances to the EDs.
\end{itemize}

@@

The queueing systems of the hospitals are designed in such a way where they can
accept two types
of individuals. 
Type 2 individuals are the ones arriving in ambulances that are allocated by
the ambulance service and 
type 1 individuals from other sources (e.g walk-in patients, urgent patients).
Each hospital may then choose to block the individuals that arrive in
ambulances when the hospital reaches a certain capacity. 
The strategy sets for each hospital is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

Both hospitals follow a queueing model with two waiting zones for 
individuals. 
The first waiting zone (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a capacity of \( N - C \), where \(N\) is the total 
capacity of the waiting space and \(C\) is the number of servers. 
% TODO: Mention what we mean by servers here?
The second waiting zone (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
EMS, stay until they are allowed to enter the first waiting zone.
The second waiting zone has a capacity of \(M\) and no servers.

@@

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % The label below Queue 1 -> Waiting zone 2
        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Waiting zone 2}};

@@

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the very start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

        % The label between the lines for T
        \node[anchor=north] at (5.15, 0.77 cm) {\small{\( T \)}};

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};
        % The label below Queue 2 -> Waiting zone 1
        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Waiting zone 1}};

@@

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model. 
    The threshold \(T\) only applies to type 2 individuals.
    If the number of individuals in waiting zone 2 is \(T\), only 
    individuals of the first type 
    are accepted (at a rate \(\lambda_1\)) and individuals of the second type 
    (arriving at a rate \(\lambda_2\)) are blocked in waiting zone 2.}
    \label{fig:diagram_of_queueing_system}
\end{figure}

Note here that both types of individuals can become lost to the system. 
An individual allocated from the ambulance service becomes lost to the system 
whenever 
an arrival occurs and the waiting zone 2 is at full capacity (\(M\) 
ambulances already parked).
Similarly, individuals get lost whenever they arrive at the waiting 
zone 1 and it is at full capacity (\(N - C\) individuals already waiting).

@@

where \(W\) is the waiting time of a potential individual, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

>>>>

\begin{itemize}
    \item the decision makers of two Emergency Departments (EDs)
    \item the Emergency Medical Services (EMS) that distribute individuals in 
    ambulances to the EDs
\end{itemize}

@@

The queueing systems of the hospitals are designed in such a way where they can
accept two types
of individuals. 
% TODO: Decide whether to define type 1, 2 only in game section, only in queueing section, or both
Type 2 individuals are defined as non-urgent patients arriving in ambulances 
that are allocated by the ambulance service and 
type 1 individuals are individuals arriving from other sources 
(e.g walk-in patients, urgent patients from either walk-ins or ambulances).
Each hospital may then choose to block type 2 individuals 
when the hospital reaches a certain capacity. 
The strategy sets for each hospital is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of hospitals \(A\) and \(B\). We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

Both hospitals follow a queueing model with two waiting zones for 
individuals. 
The first waiting zone (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of servers. 
% TODO: Mention what we mean by servers here?
The second waiting zone (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.

@@

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % The label below Queue 1 -> Parking space
        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Parking space}};

@@

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

        % The label between the lines for T
        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};
        % The label below Queue 2 -> Hospital
        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Hospital}};

@@

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model. 
    The threshold \(T\) only applies to type 2 individuals.
    If the number of individuals in the hospital is \(T\), only 
    individuals of type 1 
    are accepted (at a rate \(\lambda_1\)) and individuals of type 2
    (arriving at a rate \(\lambda_2\)) are blocked in the parking space.}
    \label{fig:diagram_of_queueing_system}
\end{figure}

Note here that both types of individuals can become lost to the system. 
An individual allocated from the ambulance service becomes lost to the system 
whenever 
an arrival occurs and the parking space is at full capacity (\(M\) 
ambulances already parked).
Similarly, type 1 individuals get lost whenever they arrive at the waiting 
space of the hospital and it is at full capacity (\(N - C\) individuals already
waiting).

@@

where \(W\) is the waiting time of a potential individual, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal \(\hat{P}\).
